%This is my curriculum vitae for a job

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\newcounter{nameOfYourChoice}
\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{ragged2e}
\usepackage[scale=0.85]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{4cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

%package for controlling tables
\usepackage{makecell}
\usepackage{multicol}
%\usepackage{hyperref}
\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{James} % Your first name
\familyname{Mba Azam} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{London School of Hygiene \& \\ Tropical Medicine (LSHTM), \\Keppel Street, \\London WC1E 7HT, \\United Kingdom.}{ }
\mobile{(+44) 7931 424395}
%\phone{(+233) 248 052090}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{james.azam@lshtm.ac.uk}
\homepage{https://jamesmbaazam.github.io/}{} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
%\section{Career Goal}
%I aim at building a professional career in the finance and insurance industry, most especially in the areas of securities, risk, and investments.
%\section{Research Interests and Career Goal}
%\cvitem{}{I have recently come to be interested in . I aim at obtaining a PhD in the said field.}
%\section{Personal Statement:}
%\cvitem{}{ I am a goal and excellence-oriented individual who has come to believe that through team work and brainstorming, milestone decisions can be made in order to achieve desired goals. Having studied with people from all over the continent and beyond, I have developed the tolerance for people from diverse cultures. As a self-motivated and responsible individual, I am loyal to the course and mission of my leadership and  supervisors. With my diverse educational background, I believe I have acquired skills and qualities which are relevant to my survival in most environments I find myself in. If need be, I take up leadership or followership roles to steer the affairs of my group without neglecting the group dynamics that come into play. I am interested in the time series dynamical modelling of childhood infectious diseases, especially measles, with a focus on the impact of outbreak response vaccination on their control.}

\section{Professional Summary}
\cvitem{}{Quantitative researcher and research software engineer with a PhD in Applied Mathematics, specialising in infectious disease modelling, outbreak analytics, and global health communication. Experienced in cross-institutional collaborations, teaching, mentoring, and developing open-source tools for real-time decision support and capacity building.}

\section{Research Interests}
\cvlistitem{Utilising mathematical and statistical models and methods to quantify the impact of outbreak response interventions to inform public health decision-making.}
\cvlistitem{Developing open-source software/tools and pipelines for reproducible outbreak response analytics.}
\cvlistitem{Investigating and contributing insights in effective science and public health policy communication.}

\section{Education}
\cventry{Feb, 2018 -- Apr, 2022}{PhD Applied Mathematics}{DSI-NRF Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA), 
Stellenbosch University}{South Africa}{}{} 
\cvitem{Thesis title}{\emph{Modelling outbreak response intervention strategies for decision-making}}
\cvitem{Supervisors}{Prof. Juliet R.C. Pulliam \& Prof. Matthew J. Ferrari}
\vspace{0.4cm}


%Sacema
\cventry{Mar, 2016 -- Mar, 2018}{MSc Mathematics}{DSI-NRF Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA), Stellenbosch University}{South Africa}{}{} 
\cvitem{Thesis title}{\emph{Assessment of a measles outbreak response vaccination campaign, and two measles parameter estimation methods}}
\cvitem{Supervisor}{Prof. Juliet R.C. Pulliam}
\vspace{0.4cm}
% AIMS-Senegal


\cventry{Aug, 2014 -- Jun, 2015}{Structured MSc Mathematical Sciences}{African Institute for Mathematical Sciences (AIMS)}{Senegal}{}{} 
\cvitem{Thesis title}{\emph{Hedging Conditional Value at Risk}}
\cvitem{Supervisor}{Dr. Maciej J. Capinski}
\vspace{0.4cm}

%undergraduate 
\cventry{Aug, 2009 -- Jun, 2013}{BSc Actuarial Science}{Kwame Nkrumah University of Science and Technology}{Ghana}{}{}
\cvitem{Thesis Title}{\emph{Predicting optimal periods for the sale of cocoa in Ghana for the year 2013, using futures contracts}}
\cvitem{Supervisor}{Mr. Vincent K. Dedu}
\vspace{0.4cm}

\section*{Professional Experience}
\cventry{Sept, 2025 -- Present}{Research Fellow}{\textit{Centre for Mathematical Modelling of Infectious Diseases}, London School of Hygiene \& Tropical Medicine}{London}{United Kingdom}{
	\textbf{Duties:}
	\begin{itemize}
		\item Developing spatial models to predict the risk of polio re-emergence and analyse eradication strategies.
		\item Analysing multi-pathogen wastewater surveillance data as part of the South African Wastewater Consortium in collaboration with the National Institute for Communicable Diseases (NICD), the South African Centre for Epidemiological Modelling and Analysis (SACEMA), the Modelling and Simulation Hub, Africa (MASHA), and the Gauteng City-Region Observatory (GCRO).
	\end{itemize}
}
\cventry{Nov, 2022 -- Aug, 2025}{Research Software Engineer}{\textit{Epiverse Initiative}, London School of Hygiene \& Tropical Medicine}{London}{United Kingdom}{
	\textbf{Duties:}
	\begin{itemize}
		\item Lead and contribute to the development and maintenance of open-source R packages for outbreak analytics, including \texttt{EpiNow2}, \texttt{epichains}, and \texttt{bpmodels}.
		\item Conduct infectious disease modelling research, including the planning, analysis, and interpretation of analyses for outbreak response and preparedness.
		\item Develop technical and non-technical resources such as R package vignettes, function references, tutorials, how-to guides, and blog posts.
		\item Provide and support outbreak analytics and data science trainings through Epiverse-TRACE.
		\item Support outbreak analytics open-source communities, including epiforecasts and epinowcast, through code contributions, code reviews, seminars, and training activities.
	\end{itemize}
}

\cventry{Mar, 2025 -- Jul, 2025}{Technical Reviewer and Video Content Creator}{Introduction to Infectious Disease Modelling for Public Health}{Epiverse TRACE Initiative Online Course}{}{
	\begin{itemize}
		\item Reviewed and edited English translations of outbreak analytics training materials originally developed in Spanish, ensuring clarity, technical accuracy, and alignment with the African context, including using examples from Africa.
		\item Created English versions of video explainers on modelling topics such as SIR models, Zika compartmental modelling, and model simulation in R, originally created in Spanish.
	\end{itemize}
}

\cventry{Feb, 2022 -- Nov, 2022}{Junior Researcher}{DSI-NRF Center of Excellence in Epidemiological Modelling and Analysis}{Stellenbosch}{South Africa}{
	\textbf{Duties:}
	\begin{itemize}
	 \item Co-developed a mathematical model of polio to provide analytics decision support to South Africa's National Advisory Group on Immunization in preparation towards a potential threat of polio re-emergence.
		\item Co-developed an analysis pipeline (using \textit{R} and \textit{GNU make}) for detecting changes in the trends of reported COVID-19 severity in South Africa.
		\item Developed a model to analyse strategies for mitigating a hypothetical pathogen in the face of emerging variants.
		\item Contributed to the activities of SACEMA Modelling and Analytics Response Team (SMART).
	\end{itemize}
}

\cventry{Feb, 2021 -- Sep, 2021}{Data Science Consultant (Part-time)}{Winning Insights and Models for Marvellous Yields (Wimmy)}{Cape Town}{South Africa}{
	\textbf{Duties:}
	\begin{itemize}
		\item Extended an existing COVID-19 model to analyse the impact of vaccine rollout in South Africa, Chile, Peru, and Zimbabwe.
		\item Contributed to a process to improve the calibration, validation, and run-time of the COVID-19 model.
		\item Led and contributed to LinkedIn articles about various health issues of immediate concern, including the potential impact of emerging COVID-19 variants, and addressing the issue of blood clotting following COVID-19 vaccination.
		\item Drafted guidelines for code testing and review within Wimmy.
		\item Contributed to the design of proposals for new analyses for Anglo America, including a study on Noise-Induced Hearing Loss among miners.
\end{itemize}}


%\subsection*{Modules Handled:}
%\cvitem{}{I helped teach the following courses to students from several departments in the university: Statistical Analysis with R, Probability, Statistics, Introductory Calculus.}
%\subsection*{Duties:}
%\cvlistitem{Offered tutorial sessions,}
%\cvlistitem{Invigilated, and graded examination papers,}
%\cvlistitem{Performed other administrative duties.}
%\subsection*{Duties:}
%\cvlistitem{I helped prepare the students for Ghana's highly competitive science and mathematics quiz competition for high school students. I performed this role for two consecutive year groups.}
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
%\section{Research competencies}
%\cvlistdoubleitem{Compartmental modelling}{Data cleaning and analysis}
%\cvlistdoubleitem{Systematic reviews}{}

\section{Research Affiliations}

\cventry{Jan, 2023 -- Present}{Research Associate}{South African Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA)}{Stellenbosch University}{South Africa}{
	Honorary affiliation in recognition of sustained contributions to SACEMA’s research and training activities. The role fosters collaborative research, training, and data sharing. 
}

\cventry{Jan, 2025 -- Present}{Senior Research Fellow}{The German West Africa Centre for Global Health and Pandemic Prevention (G-WAC)}{Kwame Nkrumah University of Science and Technology}{Ghana}{
	Honorary appointment in recognition of contributions to GWAC’s regional capacity building initiatives in infectious disease modelling and global health research. This role is aimed at facilitating collaborative research, training, and data sharing.
}


\section{Publications}

\subsection{Published}

\cvlistitem{Ward, J., Lambert, J. W., Russell, T. W., \textbf{Azam, J. M.}, Kucharski, A. J., Funk, S., ... \& Edmunds, W. J. 2025. Estimates of epidemiological parameters for H5N1 influenza in humans: a rapid review. BMC infectious diseases, 25(1), p.1755}

\cvlistitem{Austin E, S., Zheng, P., Barber, R. M., Aalipour, M. A., Aalruz, H., Ababneh, H. S., ... \& Alam, M. (2025). Global age-sex-specific all-cause mortality and life expectancy estimates for 204 countries and territories and 660 subnational locations, 1950–2023: a demographic analysis for the Global Burden of Disease Study 2023.}

\cvlistitem{Naghavi, M., Kyu, H. H., Aalipour, M. A., Aalruz, H., Ababneh, H. S., Abafita, B. J., ... \& Al Homsi, A. (2025). Global burden of 292 causes of death in 204 countries and territories and 660 subnational locations, 1990–2023: a systematic analysis for the Global Burden of Disease Study 2023. The Lancet, 406(10513), 1811-1872.}

\cvlistitem{GBD 2021 Antimicrobial Resistance Collaborators, 2024. Global burden of bacterial antimicrobial resistance 1990–2021: a systematic analysis with forecasts to 2050. \textit{The Lancet}, 404(10459), 1199-1226}

\cvlistitem{\textbf{Azam, J. M.}, Pang, X., Are, E. B., Pulliam, J. R., \& Ferrari, M. J. (2023). Modelling outbreak response impact in human vaccine-preventable diseases: A systematic review of differences in practices between collaboration types before COVID-19. Epidemics, 100720}

\cvlistitem{Kent, B. A., Holman, C., Amoako, E., Antonietti, A., \textbf{Azam, J. M.}, Ballhausen, H., \dots \& Weissgerber, T. L. (2022). Recommendations for empowering early career researchers to improve research culture and practice. \textit{PLoS biology}, 20(7), e3001680}

\cvlistitem{\textbf{Azam, J.M.}, Saitta, B., Bonner, K., Ferrari, M.J. and Pulliam, J.R. (2021). Modelling the relative benefits of using the measles vaccine outside cold chain for outbreak response. \textit{Vaccine}. DOI: 10.1016/j.vaccine.2021.08.053}

\cvlistitem{Czachur, M. V., Todd, M., Loureiro, T. G., \textbf{Azam, J. M.}, Nyeleka, S., Alblas, A., \& Davies S. J. (2021). Opening the floor for discussion: A perspective on how scholars perceive attitudes to science in policymaking in South Africa. \textit{South African Journal of Science}, 117, DOI: 10.17159/sajs.2021/7948}

\cvlistitem{\textbf{Azam, J. M.}, Are, E. B., Pang, X., Ferrari, M. J., \& Pulliam, J. R. (2020). Outbreak response intervention models of vaccine-preventable diseases in humans and foot-and-mouth disease in livestock: a protocol for a systematic review. \textit{BMJ open}, 10(10), DOI: http://dx.doi.org/10.1136/bmjopen-2019-036172}

\cvlistitem{Lukwa, A. T., Siya, A., Zablon, K. N., \textbf{Azam, J. M.}, \& Alaba, O. A. (2020). Socioeconomic inequalities in food insecurity and malnutrition among under-five children: within and between-group inequalities in Zimbabwe. \textit{BMC Public Health}, 20(1), DOI: https://doi.org/10.1186/s12889-020-09295-z}

\subsection{In review}

\cvlistitem{Cuartero et al (2025). The impact of ambiguously reported epidemiological parameters for infectious disease modelling and recommended best practices}

\subsection{In preparation}

\cvlistitem{Azam et al (2025). Daily versus Weekly Data in Epidemiological Forecasting: Computational and Practical Implications}

\subsection{Media}
\cvlistitem{Forbes.com. Will Coronavirus Measures Slow The Spread Of Measles? Ask This Ghanaian. Jul 2020. URL: \url{https://www.forbes.com/sites/andrewwight/2020/07/29/will-coronavirus-measures-slow-measles-ask-this-ghanaian/}}


\section{Fellowships, Honors, and Awards}
\cventry{Sept, 2020 \& Sept, 2021}{Best student oral presentation}{DSI-NRF SACEMA Research Days}{}{}{}
\cventry{Dec, 2019}{Stellenbosch University Library Open Access Fund}{\pounds 405}{}{}{A competitively awarded subsidy towards an Open Access Publication fee.}
\cventry{May, 2019}{Professional Certificate Program in Health and Humanitarian Supply Chain Management}{\$5,000/6,000 of course fee waived}{Georgia Tech Center for Health \& Humanitarian Systems}{Georgia, United States}{A course fee waiver awarded competitively. I could not attend because of unforeseen circumstances.}

\cventry{Oct, 2018}{Big Data Policy Fellowship}{\pounds 4000}{Development in Africa with Radio Astronomy (DARA)}{University of Manchester, United Kingdom}{A one month fellowship that provided training in science and policy communication in the context of Big Data projects and in particular, the Square Kilometre Array in South Africa and Australia.}

\cventry{Feb, 2018}{PhD Bursary}{R 140, 000}{DSI-NRF South African Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA)}{Stellenbosch University}{South Africa}{}

\cventry{Aug, 2017}{Best student oral presentation}{DSI-NRF SACEMA Research Days}{}{}{}

\cventry{Feb, 2016}{Masters Bursary}{R 120, 000}{DSI-NRF SACEMA}{Stellenbosch University}{South Africa}{}

%\subsection{Working Papers}
%
%\cvitem{}{\textbf{Azam, J. M.}, Pulliam, J. R. C., \& Ferrari, M. J. Modelling the use of vaccination and non-pharmaceutical interventions to mitigate an infectious disease outbreak in the face of an emerging variant.}

\section{Presentations}
\subsection{Conference Oral Presentations}

\cvitem{Apr, 2025}{\texttt{epichains}: an R package for analysing transmission chains data. \textit{Humanitarian Modelling Dialogue Workshop, WHO Pandemic Hub, Berlin, Germany}}

\cvitem{Nov, 2024}{Benchmarking time-varying reproduction number, $Rt$, and forecasting models - a case study of the \texttt{EpiNow2} R package. \textit{Infectious Disease Modelling (IDM) Conference, Bangkok, Thailand}}

\cvitem{Aug, 2023}{Superseding R packages – lessons learned from transitioning to the \texttt{epichains} R package from \texttt{bpmodels}. \textit{Research Software London Southeast conference, Imperial College, London, United Kingdom}}

\cvitem{Nov, 2021}{\textbf{JM Azam}, MJ Ferrari, JRC Pulliam. Modelling the relative benefits of using the measles vaccine outside cold chain for outbreak response. \textit{Epidemics8, Elsevier (Virtual presentation)}}

\cvitem{Oct, 2019}{\textbf{JM Azam}, MJ Ferrari, JRC Pulliam. Measles outbreak response: is it worthwhile to use the vaccine outside of the cold chain?. \textit{Modelling in the Context of African Health (MoCAH)}, Durban, South Africa.}

\cvitem{Sept, 2019}{\textbf{JM Azam}, P Xiaoxi, AB Elisha, MJ Ferrari, JRC Pulliam. Outbreak response models of human vaccine preventable diseases (1970-2019) - A systematic review. \textit{DSI-NRF SACEMA Research Days (PhD Student Presentation)}, Stellenbosch, South Africa.}

\cvitem{Sept, 2017}{\textbf{JM Azam}, JRC Pulliam. Measles in a school in Stellenbosch, South Africa. \textit{DSI-NRF SACEMA Research Days (MSc Student Presentation)}, Stellenbosch, South Africa.}

\subsection{Invited Talks}
\cvitem{Nov, 2024}{Epiverse-TRACE: Advancing and Enabling Collaborative Open-Source R Tools for Outbreak Analytics, JUNIPER Weekly Seminar (virtual)}

\cvitem{Nov, 2024}{Summary of analytical and statistical tools available for modelling pandemic H5N1 containment and mitigation, WHO R\&DBlueprint Virtual Consultation}

\cvitem{Sept, 2024}{Mpox 2024 outbreak: Common analytics tasks and available R tools/packages, UK Pandemic Sciences Network}

\cvitem{Sept, 2024}{Mpox 2024 outbreak: Common analytics tasks and available R tools/packages, World Health Organisation Mpox Analytics Collaboratory Seminars}

\cvitem{Jun, 2022}{\textit{Modelling outbreak response strategies for decision-making} (\textit{Presented virtually}), Center for Epidemiological Modelling and Analysis, University of Nairobi, Kenya.}

\cvitem{Jul, 2020}{\textit{Modelling the benefits of using the measles vaccine outside cold chain for outbreak response}, Médecins Sans Frontières (MSF) Vaccine Working Group meeting (Presented virtually)}

\cvitem{Apr, 2019}{\textit{Measles outbreak response vaccination: the role of the vaccine supply chain in low-income settings}, Department of Logistics, Stellenbosch University}

\subsection{Poster Presentations}
\cvitem{Dec, 2019}{\textbf{JM Azam}, MJ Ferrari, JRC Pulliam. A framework for evaluating vaccine delivery strategies for responding to measles outbreaks in hard-to-reach populations. \textit{Epidemics7, Charleston, United States (Presented on my behalf).}}

\cvitem{Sept, 2018}{\textbf{JM Azam}, JRC Pulliam. Measles outbreak response vaccination: how can we optimize the vaccine supply chain for efficient responses?. \textit{DSI-NRF SACEMA Research Days (PhD Student Presentation)}, Stellenbosch, South Africa.}

\cvitem{Jun, 2016}{\textbf{JM Azam}, MI Andersson, E du Toit, M Nieuwoudt. Modelling Hepatitis B Transmission in sub-Saharan Africa - A Focus on the Impact of Vaccination Within Existing HIV MTCT Infrastructure. \textit{Meaningful Modelling of Epidemiological Data, MMED (Student Presentation)}, African Institute for Mathematical Sciences (AIMS), Muizenberg, South Africa.}

%\cventry{Jul -- Aug, 2012}{Intern}{State Insurance Company (S.I.C), Life Section}{Sunyani}{Ghana}{\textbf{Roles:} I performed underwriting as well as front desk duties such as processing policy forms, claims, and registering customer complaints.}
%
%\cventry{Jan -- Aug, 2012}{Creative Director}{Royal Diadem Magazine}{Kwame Nkrumah University of Science and Technology}{Ghana}{\textbf{Roles:} I was in charge of supervising and communicating the desired design of the digital and print media.}
%
%\cventry{Jun, 2012 \& Jun, 2013}{Co-Trainer of Contestants}{National Science and Mathematics Quiz}{St. Francis Xavier Minor Seminary}{Ghana}{}
%------------------------------------------------

\section{Panel Discussions}
\cvitem{Nov, 2024}{\textbf{WHO R\&DBlueprint Virtual Consultation.} \textit{Preparing for containment and mitigation of pandemic H5N1 influenza.} We discussed gaps in our knowledge and Present approach to tackling a potential H5N1 widespread outbreak.}

\cvitem{Jul, 2023}{\textbf{Health Data Research UK Black Internship Programme.} \textit{Career Panel.} We shared our career journeys and experiences, and answered questions from the mentees.}

\cvitem{Dec, 2020}{\textbf{The New African Scientist.} \textit{STEM - For Us, By Us conference, Visibility STEM Africa.} We discussed on topics including the future of the academic/research environment in Science Technology Engineering Mathematics (STEM) in Africa, mental health among young African researchers, how we find the motivation to do work outside of research, and our vision for STEM in Africa in the next few years.}

\cvitem{Dec, 2018}{\textbf{Science Communication for Policy Engagement.} \textit{Science Forum South Africa (SFSA), CSIR International Convention Centre, Pretoria, South Africa.} We discussed the relationship between science communication and science engagement, and the challenges that early career researchers face in communicating the policy implications of their research. We also discussed (South) Africa's readiness for the Fourth Industrial Revolution and the emerging challenges.}

\section{Teaching Experience}
\cventry{June, 2025}{Co-lead facilitator}{Outbreak Data Science for Lab Scientists: A Hands-On Introduction with the Epiverse R Package Ecosystem}{KEMRI Wellcome Trust Research Programme}{Kilifi, Kenya}{}
\cventry{Sept, 2024}{Lead facilitator}{Modelling for Pandemic Preparedness and Response}{German West African Center for Global Health and Pandemic Prevention}{Kwame Nkrumah University of Science and Technology, Ghana}{}

\cventry{Aug, 2022}{Co-lead facilitator}{Introduction to R: Management, Exploration, and Communication of Data}{SACEMA}{South Africa}{}

\cventry{Oct, 2017; May, 2018 \& 2019}{Tutor (assistant)}{Introduction to R: Management, Exploration, and Communication of Data}{SACEMA}{South Africa}{}

\cventry{Aug, 2016 -- Jun, 2017}{Teaching assistant}{Introductory Calculus and Algebra}{Department of Mathematical Sciences, Stellenbosch University}{South Africa}{}

\cventry{Sept, 2013 -- Jul, 2014}{Teaching assistant}{Introductory Probability and Statistics, and R for Statistical Analyses}{Department of Mathematics, Kwame Nkrumah University of Science and Technology}{Ghana}{}

\section{Student Supervision and Mentoring}
\cventry{Jul, 2025 -- Aug, 2025}{Supervisor}{Health Data Research UK Black Internship Programme}{London School of Hygiene \& Tropical Medicine}{United Kingdom}{I am supervising an intern over an 8-week period to develop applied skills in infectious disease forecasting and evaluation through a project assessing the performance of COVID-19 forecasts in the UK using \texttt{R}, \texttt{EpiNow2}, and \texttt{scoringutils}.}{}
\cventry{Jul, 2024 -- Aug, 2024}{Mentor}{Health Data Research UK Black Internship Programme}{London School of Hygiene \& Tropical Medicine}{London, United Kingdom}{For 8 weeks, I mentored an intern by providing advice on career trajectories, how to effectively conducting his research, and personal development in preparation for PhD studies.}{}
\cventry{Apr, 2023 -- Jun, 2023}{Mentor}{Research Software Camp}{The Software Sustainability Institute }{United Kingdom}{In 3 months, I mentored a PhD student to develop a working knowledge of using R for running generalised linear mixed models. We worked our way up from no knowledge of R to running and interpreting regression models.}{}

%\section{Committees \& Working Groups}
%\cventry{Nov, 2022 -- Nov 2023}{Member}{Equity, Diversity, Inclusion, and Accessibility sub-committee}{Society of Research Software Engineering}{United Kingdom}{}{}
\section{Professional Development}

\subsection{Workshops and Trainings}
\cventry{Dec, 2025 -- Feb, 2026}{Diversifying Leadership Programme}{Advance HE}{London}{}{A 3-month leadership course that equipped me with a mindset to navigate institutional power dynamics by leveraging cultural capital and strategic networking. Developed practical skills in using Action Learning Sets to solve complex leadership challenges and refined a personal leadership story for increased visibility.}

\cventry{Apr, 2025}{Humanitarian Modelling Dialogue Workshop}{WHO Pandemic Hub}{Berlin}{Germany}{I co-facilitated a hackathon on software tools for rapid outbreak analytics during humanitarian crises.}

\cventry{Feb, 2025}{UK Epidemic Analytics and Modelling Meeting}{London School of Hygiene \& Tropical Medicine (HPRU in Health Analytics and Modelling)}{London}{United Kingdom}{This was a 2-day meeting of modellers from across the UK to network and brainstorm the way forward with pro-active preparedness towards a more efficient epidemic analytics in the UK.}

\cventry{Nov, 2024}{Understanding, evaluating, and improving forecasts of infectious disease burden}{Infectious Disease Modelling Conference}{Bangkok}{Thailand}{This was a half-day pre-conference workshop.}

\cventry{Apr, 2024}{R Developer Day}{Imperial College}{London}{United Kingdom}{An open, collaborative event for people interested in contributing to base R. I worked with two others to submit a patch for an improvement to the base package's substr() and substring() functions to help clarify their similarities and differences and demonstrate some previously obscure features.}

\cventry{Dec, 2023}{Curriculum development workshop for the short course, ``Modelling for Pandemic Preparedness and Response''}{German-West African Centre for Global Health and Pandemic Prevention/Technische Universität Berlin}{Berlin}{Germany}{This workshop involved a meeting of experts to design the named two week short course to be offered in Ghana.}

\cventry{Jul, 2023}{RSLondonSouthEast 2023}{Imperial College London}{London}{United Kingdom}{This workshop aimed to provide a regional focus on research software activities, offer an opportunity to present work to a regional audience, and help participants develop links with the wider Research Software Engineering community.}

\cventry{Mar, 2023}{Forecasting natural and social systems}{The Royal Society}{London}{United Kingdom}{This meeting aimed to convene leading experts in forecasting across disciplines to discuss the predictability of different systems, to exchange expertise, and to identify common challenges and possible solutions.}

\cventry{Dec, 2022}{100 days and 100 lines of code}{Epiverse Initiative, London School of Hygiene \& Tropical Medicine}{London}{United Kingdom}{}

\cventry{Oct, 2022}{Measles modelling workshop}{Vaccine Impact Modelling Consortium}{Virtual}{}{}

\cventry{Nov, 2020}{FameLab - Science Communication Competition}{DSI-NRF Center of Excellence in Epidemiological Modelling and Analysis}{Stellenbosch, South Africa}{}{}

\cventry{Jan, 2020}{Software Engineering for Applied Mathematical Sciences}{SACEMA}{Stellenbosch}{}{}

\cventry{Nov, 2019}{The Annual African Vaccinology Course}{Vaccines for Africa Initiative (VACFA)}{University of Cape Town, South Africa}{}{}

\cventry{Feb, 2019}{FameLab - Science Communication Competition}{DSI-NRF Center of Excellence in Epidemiological Modelling and Analysis}{Stellenbosch, South Africa}{}{}

\cventry{May, 2018}{The Conversation Writing Workshop}{Stellenbosch University}{South Africa}{}{}

\cventry{Dec, 2017}{FameLab - Science Communication Competition}{CSIR International Convention Centre}{Pretoria, South Africa}{}{}

\cventry{Dec, 2017}{Spatial Disease Mapping}{University of Cape Town}{Cape Town}{}{}

\cventry{Nov, 2017}{The Use of Measles Vaccines Under Extended Controlled Temperature Conditions}{Medicins sans Frontieres}{Paris, France}{}{}

\cventry{May, 2017}{Data Science}{AIMS-South Africa}{Muizenberg, Cape Town, South Africa}{}{}
\cventry{Aug, 2016}{Science Communication and Public Engagement}{AIMS-South Africa}{Muizenberg, Cape Town, South Africa}{}{}

\cventry{Jul, 2016}{Clinic on the Meaningful Modeling of Epidemiological Data (MMED)}{University of Florida, SACEMA-Stellenbosch University, AIMS-South Africa}{Muizenberg, Cape Town, South Africa}{}{}

\cventry{May, 2016}{Global Change Impact on Infectious Diseases and Alien Species Expansion}
{AIMS-South Africa in collaboration with 16 other societies/organisations}{}{}{}%{The main objectives of the workshop was to network communities coming from different backgrounds (biology, mathematical sciences, medicine, social sciences and global environment change) and different parts of the world, and having an interest in the study and control of epidemic diseases and invasive species.}
\cventry{Jul, 2015}{Computing in Applied Mathematical Sciences (CAMS)}
{AIMS-Ghana}{}{}{}%{This was a 2-week biomathematics workshop. The major concentration was on how to simulate models for diseases such as Dengue Fever, HPV, HIV/AIDS, and so on, in Python and R.}


\subsection{Short Courses}
\cventry{Sept, 2023}{Equality \& Diversity Essentials}{London School of Hygiene \& Tropical Medicine}{London}{}{}
\cventry{Nov, 2022}{GDPR Compliance: Essential Training}{LinkedIn Learning}{}{}{}
\cventry{Nov, 2020}{Learn to write for the media}{The Conversation Africa}{}{}{An online course that teaches the basics of how to write media/popular articles based on scientific findings.}
\cventry{Dec, 2019}{Science Communication Master Class}{Stellenbosch University}{Stellenbosch}{}{}
\cventry{Jul, 2018}{The Systematic Review}{African Doctoral Academy}{Stellenbosch University}{South Africa}{}
\cventry{May, 2018}{Individual-based Modelling in Epidemiology - A Practical Introduction}{SACEMA}{Stellenbosch University}{South Africa}{}
\cventry{August, 2017}{Introduction to Scientific Writing Skills}{The Writing Center}{Stellenbosch University}{South Africa}{}
\cventry{Oct, 2016}{Bayesian Analysis of Longitudinal Data}{SACEMA}{Stellenbosch University}{South Africa}{}
\cventry{Sept, 2016}{Mathematical Modeling of Infectious Diseases (MMID)}{University of Cape Town}{Cape Town, South Africa}{}{}
\cventry{Mar - Aug, 2016}{Introduction to Epidemiology and Research Methodology}{SACEMA}{Stellenbosch University}{South Africa}{}
\cventry{May, 2016}{Applying Quantitative Bias Analysis to Epidemiologic Data}{SACEMA}{Stellenbosch University}{South Africa}{}
\cventry{March, 2016}{Bayesian Biostatistics}{SACEMA}{Stellenbosch University}{South Africa}{}

\section{Peer Review}

\cvlistdoubleitem{Scientific Reports}{Journey of Open Science Software}
\cvlistdoubleitem{PLOS Global Health}{Bulletin of Mathematical Biology}

\section{Open Source Contributions}
\cventry{Nov 2022 -- Present}{Developer \& maintainer}{\texttt{epichains} \& \texttt{bpmodels}}{}{}{R packages for simulating and analysing transmission chains using branching process models.}
\cventry{Nov 2022 -- Present}{Co-maintainer}{\texttt{EpiNow2}}{}{}{R package for estimating real-time infectious disease cases and time-varying epidemiological parameters.}
\cventry{2023 -- Present}{Contributor}{\texttt{epinowcast}, \texttt{primarycensored}, and \texttt{scoringutils}}{}{}{R packages for forecasting and nowcasting real-time infectious disease cases and time-varying epidemiological parameters, and evaluation of forecasts.}

\section{Technical Competencies}
\cvitem{Programming tools}{R, Stan, Bash, GNU Make, Github \& Git}
\cvitem{Dashboard tools}{RShiny, Quarto Dashboards}
\cvitem{Markup languages}{{\tiny}LaTeX, Markdown, R Markdown, HTML}
%\cvitem{Spreadsheet}{MS Excel, Google sheets}
\cvitem{Operating Systems}{MacOS, Linux/Ubuntu, Microsoft Windows}
\cvitem{Presentation}{Quarto Presentations, MS PowerPoint, LaTeX Beamer}
\cvitem{Project management}{Agile/scrum}
\cvitem{Graphic Design}{Inkscape, Adobe suite, Camtasia, Canva, CapCut}

%----------------------------------------
%\cventry{2013}{Chair of Vetting committee for Executive Position Aspirants}{Department of Actuarial Science, KNUST}{Kumasi}{Ghana}{}
%\cventry{2012}{Committee member}{Pax Romana Choir Technical Committee, KNUST}{Kumasi}{Ghana}{}
%\cventry{2012}{Committee member}{Pax Romana Choir Second Album Production, KNUST}{Kumasi}{Ghana}{}
%\cventry{2012}{Committee member}{Pax Choir 25th Anniversary Educational Project, KNUST}{Kumasi}{Ghana}{}
%\cventry{2012}{Volunteer}{Pax Romana Freshers Orientation, KNUST}{Kumasi}{Ghana}{}
%\cventry{2011}{Committee member}{Pax Romana Dinner Planning, KNUST}{Kumasi}{Ghana}{}
%\cventry{2010}{Volunteer}{University Freshers Orientation, KNUST}{Kumasi}{Ghana}{description}

%\section{Competitions}
%\cvitem{Aug, 2019}{\textbf{Participant, Stellenbosch University Hackathon, in partnership with Innovus and sponsored by Entersekt, Capitec Bank, and Explore} My team of three successfully reclassified an underclassified group of transactions and suggested a loan service to help customers replace their old appliances with new ones to save electricity and the environment.}
%\cvitem{Feb, 2018}{\textbf{Runner up (alongside two others), Famelab organised by SACEMA, Stellenbosch University, a science communication competition run by the British Council, Jive media, and SAASTA.} I advanced past the initial rounds but was eliminated in the final heat.}
%\cvitem{Dec, 2017}{\textbf{Heat finalist, Famelab, a science communication competition organized by the British Council, Jive media, and SAASTA.}}
%\cvitem{Jun, 2009}{\textbf{Contestant, National Science and 
%Mathematics Quiz, Ghana.} My team was eliminated in 1/16th stage of competitions.}

%\section{Memberships}
%\cvitem{Jan, 2019 - Present}{Southern Africa Mathematical Sciences Association (SAMSA)}

\section{Positions of Responsibility}
\cventry{Dec, 2025 -- Present}{Elected Chair}{Black Early Career Staff Network}{London School of Hygiene \& Tropical Medicine}{London}{United Kingdom}{}
\cventry{Apr, 2025 -- Dec, 2025}{Acting Chair}{Black Early Career Staff Network}{London School of Hygiene \& Tropical Medicine}{London}{United Kingdom}{}
\cventry{Jul, 2020 -- Jul, 2021}{President}{Association of Ghanaian Students in Stellenbosch University}{Stellenbosch University}{South Africa}{}{}
\cventry{Jun, 2019 -- Jun, 2020}{Vice President}{Association of Ghanaian Students in Stellenbosch University}{Stellenbosch University}{South Africa}{}{}
\cventry{2017}{Student Representative}{SACEMA Research Days planning committee}{Stellenbosch University}{South Africa}{}
\cventry{2017}{Student Representative}{SACEMA Strategic Planning Meeting}{Stellenbosch University}{Stellenbosch University}{}
\cventry{2009 -- 2013}{Member of Several committees}{Pax Romana Local and Pax Romana Choir}{Kwame Nkrumah University of Science and Technology}{Ghana}{} 

\section{Diversity, Equity, and Inclusion}
\cventry{Jan, 2025 -- Present}{Lead and Acting Chair}{Black Early Career Staff Network Formation Task Force}{London School of Hygiene \& Tropical Medicine, London, Untied Kingdom}{}{}{}
\cventry{Dec, 2022 -- Oct 2023}{Active Member}{Equity, Diversity, Inclusion, and Accessibility Working Group}{Society of Research Software Engineering}{United Kingdom}{}{}
\cventry{Jun, 2023 - Sept, 2023}{Career Panel Member}{Health Data Research UK Black Internship Programme}{London School of Hygiene \& Tropical Medicine}{United Kingdom}{}{}

\section{Professional Memberships}
\cventry{Sept, 2024 -- Present}{Affiliate Member}{Joint UNIversities Pandemic and Epidemiological Research (JUNIPER)}{}{United Kingdom}{}{}
\cventry{Dec, 2022 -- Present}{Member}{Society of Research Software Engineering}{}{United Kingdom}{}{}
\cventry{Sep, 2023 -- Present}{Member}{Models of Infectious Disease Agent Study (MIDAS)}{}{University of Pittsburgh}{US}{}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{Communication Skills}

%\cvlistitem{I am a good public speaker, and a sharer of knowledge. I have a sound command of the English Language.}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
%\section{Languages}
%
%%\cvitemwithcomment{}{English (fluent in both written and spoken), basic conversational French, Kusasi(mother tongue), Twi (fluent in both written and spoken)}{}
%\cvitemwithcomment{English}{Fluent both in speaking and writing}{}
%%\cvitemwithcomment{French}{Basic conversational}{}
%\cvitemwithcomment{Twi}{Fluent both in speaking and writing}{}
%\cvitemwithcomment{Kusasi}{Basic in speaking}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
%\section{Hobbies}
%
%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
%%\cvlistitem{Sports: Volleyball, Basketball, Swimming, Playing the Guitar, Word Games, Reading Musical Scores, Listening to Classical Music, Reading Cross-disciplinary materials, and Travelling.}
%\cvlistdoubleitem{YouTuber}{Blogger}
%\cvlistdoubleitem{Photographer}{Musician (Guitar)}


%----------------------------------------------------------------------------------------
% REFEREES
%----------------------------------------------------------------------------------------

\section{Referees}
\qquad \qquad \qquad \qquad \qquad Available upon request.

%\begin{multicols}{2}
%	1. Prof. Juliet Pulliam, \\ 
%	DSI-NRF Centre of Excellence \\  
%	in Epidemiological Modelling \\ 
%	and Analysis (SACEMA),\\
%	Stellenbosch University \\
%	\textbf{Email:} pulliam@sun.ac.za}
%	\columnbreak
%	2. Prof. Matthew J. Ferrari, \\
%	Pennsylvania State University, \\
%	Center for Infectious Disease Dynamics, \\ 
%	United States. \\
%	\textbf{Email:} mjf283@psu.edu} 
%\end{multicols}

%\cvitem{}{
%	\begin{minipage}[l]{0.4\textwidth}
%	1. Prof. Juliet R.C. Pulliam, \\
%	DSI-NRF Centre of Excellence \\
%	in Epidemiological Modelling \\
%	and Analysis (SACEMA),\\
%	Stellenbosch University \\
%	\textbf{Email:} pulliam@sun.ac.za
%\end{minipage}
%\hfill
%\begin{minipage}[l]{0.6\textwidth}
%	2. Prof. Matthew J. Ferrari, \\
%	Center for Infectious Disease Dynamics, \\
%	United States. \\
%	Pennsylvania State University \\
%	\textbf{Email:} mjf283@psu.edu	
%\end{minipage}	
%}
\end{document}